---
title: "Loan Data"
author: "Logan Roe"
date: "2023-08-24"
output: html_document
---

**IMPORT LIBRARIES**

```{r}
library(tidyverse)
```

```{r}
df = read.csv("C:/Users/Logan/Documents/GitHub/bootcamp/week_7/loan_project/Anonymize_Loan_Default_data.csv",stringsAsFactors=FALSE, fileEncoding="latin1")
```

![]()

```{r}
?read.csv
```

```{r}

```

**Tidy Data**

*drop X column*

*drop first row*

*data types follow format*

checkand replace nulls

```{r}
df <- select(df, -X)
```

```{r}
df <- select(df, -zip_code)
```

```{r}
df <- select(df, -next_pymnt_d)
```

```{r}
df <- select(df, -mths_since_last_delinq)
```

```{r}
df <- filter(df, id!= 2)

```

```{r}
glimpse(df)
```

```{r}
df %>% summarize(na_count = sum(is.na(df)))
colSums(is.na(df))

```

After Investigating the NULL Values we dropped the problem variables to maintain the majority of our data.

```{r}
df = na.exclude(df)
```

**EXPLORE**

Gather information:

Decide on independent/dependent variables

Decide on stat/model test

Descriptive Statistics

Visualization of Columns

####Deciding on Independent and Dependent Variables:

interest rate impacts term length

there isnt a significant relationship between the interest rate and the term length.

there is a significant relationship between the interest rate and the term length.

```{r}
ggplot(df)+
  geom_bar(aes(term))
```

```{r}
ggplot(df)+
  geom_bar(mapping= aes(log(int_rate)))
```

```{r}
ggplot(df)+
  geom_point(mapping = aes(installment,int_rate))
```

```{r}
cor(df$installment,df$int_rate)
```

```{r}
ggplot(df)+
  geom_point(mapping = aes(annual_inc,int_rate))
```

```{r}
ndf <- select_if(df, is.numeric)
```

```{r}
round(cor(ndf), 2)

```

Gather stats on Int_Rate on the column

```{r}
summary(df$int_rate)
```

**ANALYZE**

build

```{r}
glm(df$total_pymnt~df$int_rate)
```
