
### Homework

1.  Do 5 CodeWars problems in R. Share your solutions here:

    ```{r}
    # Problem 1 I solved in R:
    # Write the solution

    # Pr
    ```

2.  Create a function that checks an input of type `int` and returns
    fizz if the number is a multiple of 3, buzz if the number is a
    multiple of 5, and fizzbuzz if the number is a multiple of 3 and 5.

    ```{r}

    ```

3.  **Mario Challenge:** In the classic Super Mario games, Mario ends
    each level by ascending a flight of stairs and leaping off the top
    to arrive at the castle at the end. (See
    [here](https://youtu.be/-avspZlbOWU?t=55) for details). We can
    imagine that each of the bricks of the stairs is a character X.
    Create a function that prints out a set of stairs. For example:

    If the function is called marioStairs() and we pass in the value 4,
    we would expect to see stairs with a length of 4 and a height of 4:

    X

    XX

    XXX

    XXXX

    ```{r}
    # You may feel more comfortable figuring this out in Python first, then translating into R later.
    ```

4.  Find a built-in dataset you would like to explore. Explore the
    dataset and use the cheat sheet you built in Week 1 to label
    continuous and discrete data. Analyze the dataset using dplyr,
    create graphs, mutate two columns, and formulate a hypothesis about
    your data.

#### **Data Types:**

-   Column 1: Data Type

-   Column 2: Data Type

```{r}

```

```{r}

```

```{r}

```

```{r}

```
