## Homework

1.  Create an array of two 3x3 matrices from the given vectors.

    ```{r}
    vec1 <- c(1, 2, 3, 4, 5, 6, 7, 8, 9)
    vec2 <- c(10, 11, 12, 13, 14, 15, 16, 17, 18)
    matrix1 <- matrix(
              vec1,
              nrow =3,
              ncol =3,
            )
            
            
    matrix2 <- matrix(
              vec2,
              nrow =3,
              ncol =3,
            )
    
    matrix1
    matrix2
    ```

2.  In the above matrix that you created, print the value 5 by indexing in to the matrix.

    ```{r}
matrix1[2,2]
    ```

3.  Print the third row of the first matrix.

    ```{r}
matrix1[3,]
    ```

4.  Print the second column of both matrices.

    ```{r}
matrix1[,2]
matrix2[,2]
    ```

5.  Create two strings with your first and last name, respectively. Then concatenate them, and print the new value as "My name is \<your newly created concatenated variable will go here\>"

    ```{r}
str1 <- "Logan"
str2 <- "Roe"
str3 <- paste(str1,str2)
sprintf("My name is %s", str3)
    ```

6.  What values can a BOOLEAN contain?

    ```{r}
sprintf("BOOLEAN are %i or %i , also known as %s or %s", TRUE, FALSE, 'TRUE','FALSE')
    ```
